\documentclass[11pt]{amsart}
\usepackage{graphicx}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage[a4paper,margin=1in]{geometry} 
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{positioning,calc}

% TODO
\hbadness=10000

\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\DeclarePairedDelimiter\fracpart{\{}{\}}

\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\paren}[1]{\left(#1\right)}
\newcommand{\Int}[1]{\mathbb Z_{#1}}
\newcommand{\Intbar}[1]{\Bar{\mathbb Z}_{#1}}
\newcommand{\Unit}[1]{\Int{#1}^\times}

\newcommand{\prob}{\mathbb{P}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Zko}{\mathbb{Z}_{k+1}}
\newcommand{\Zp}{\mathbb{Z}_p}
\newcommand{\rbf}{\mathbf{r}}
\newcommand{\abf}{\mathbf{a}}
\newcommand{\vbf}{\mathbf{v}}
\newcommand{\Vbf}{\mathbf{V}}
\newcommand{\ubf}{\mathbf{u}}
\newcommand{\Ubf}{\mathbf{U}}
\newcommand{\wbf}{\mathbf{w}}
\newcommand{\Wbf}{\mathbf{W}}
\newcommand{\Ibar}{\Bar{I}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{claim}[theorem]{Claim}

\title{Eleven, twelve and thirteen lonely runners}
\author[T. Sungkawichai]{Touch Sungkawichai}
\date{\today}
\address{London, UK}
\email{touchsungkawichai@gmail.com}
\author[T. Trakulthongchai]{Tanupat Trakulthongchai}
\address{St John's College, University of Oxford, Oxford, UK}
\email{tanupat.trakulthongchai@sjc.ox.ac.uk}
\date{\today}
\subjclass[2020]{11K60}

\begin{document}
\maketitle
\begin{abstract}
    Wills stated the Lonely Runner Conjecture: if $k+1$ runners run with distinct and constant speeds around a unit circle from a 
    common starting point, each runner is at least $1/(k+1)$ away from every other runner at some point in time.
    A computational method developed by Rosenfeld and the second author verified the conjecture for up to $10$ runners.
    We refine the method to provide computer-assisted proofs of the Lonely Runner Conjecture for $11$ and $12$ runners.
\end{abstract}

\section{Introduction}
The Lonely Runner Conjecture arose in the study of Diophantine approximation \cite{Wills},
though it has been interpreted in the context of view obstruction/Billiard trajectory 
\cite{cusick1984view}, covering radius of zonotopes \cite{henze_covering_2017}, and the chromatic number of a 
distance graph \cite{zhu2002circular}. 
It was conjectured independently by Wills \cite{Wills} in 1967 and Cusick\cite{cusick1984view} in 1984. 
Popularly, the conjecture asserts that if $k+1$ runners run with distinct,
constant speeds around a unit circle, each of them will be \emph{lonely} at some time. 
Being lonely here means that every other runner is at least $\frac{1}{k+1}$ away from that runner. 
Formally, by letting $\norm{\cdot}$ denote the distance to the nearest integer, the Lonely Runner Conjecture is stated as follows.

\begin{conjecture}
  \label{lonelyconj}
  Let $u_1,\ldots,u_{k+1}$ be distinct real numbers. There is a real number $t$ such that
\[
  \norm{t u_i-tu_j} \ge \frac{1}{k+1}
\quad \text{for all } i \neq j.
\]
\end{conjecture}
The lower bound of $\frac{1}{2k}$ follows immediately from the union bound. 
Significant asymptotic improvements were due to Pararnau and Serra \cite{perarnau_correlation_2016}, Tao \cite{Tao}, 
and lastly Bedert \cite{bedert_riesz_2025}, who, in November 2025, gave the present lower bound of 
$\frac{1}{2k}+\frac{1}{k^{5/3+o(1)}}$.

On the other hand, the conjecture has also been addressed from the ground up by proving it for small numbers of runners. 
The conjecture is currently known to hold for $k+1\leq10$. From now on, we will restrict our attention to this direction;
see the review of Perarnau and Serra \cite{perarnau_lonely_2025} for a broader perspective.

The two smallest cases for $k$ are trivial. Proofs of the next two were given by Betke and Wills \cite{fourrunners},
and Cusick and Pomerance \cite{cusick1984view}, respectively. In the same paper that proved the case $k=5$, Bohman, Holzman,
and Kleitman~\cite{Bohman} showed that it suffices to consider integer speeds, transforming the problem from a continuous one 
to a discrete one. This reduction, combined with fixing the speed of the slowest runner to be $0$, produces the following useful
equivalent statement to Conjecture \ref{lonelyconj}. We refer to the vector $\ubf=(u_1,\ldots,u_k)$ as a \emph{speed set}.

\begin{conjecture}
    Any $\ubf\in\Z_{>0}^k$ has the \emph{LR property}, that is, there is a real number $t$ such that
    \[\norm{tu_i}\geq\frac{1}{k+1} \quad \text{for all } i = 1,\dots,k+1.\] 
    
    We denote this statement by $LRC(k)$.
\end{conjecture}

Before 2025, the conjecture was known to be true for $k\leq6$, where the final case was proven by Barajas
and Serra \cite{barajas_lonely_2008} in 2008. In September 2025, Rosenfeld \cite{Rosenfeld} introduced a computational 
method that settled $k=7$ (and later $k=8$ \cite{rosenfeld_lonely_2026}). In doing so, he relies on the finite-checking
result of Malikiosis, Santos, and Schymura \cite{Malikiosis}, which follows similar results of Tao \cite{Tao} and
Giri and Kravitz \cite{giri_structure_2026}. 
The second author \cite{Trakulthongchai} subsequently refined this method to prove the conjecture for $k=8,9$ in November 2025.

In this paper, we further develop this computational method to verify the Lonely Runner Conjecture for $k=10$ and $11$. 
Our overall strategy is outlined in the next section where we provide more context of the computational method of \cite{Rosenfeld} 
and \cite{Trakulthongchai}. 
Sections \ref{sec:quotient}, \ref{sec:sieves} and \ref{sec:onetok} explain the techniques that helped us simplify our verification.
Section \ref{sec:algo} summarizes the algorithm that we implemented, the results of which are presented in Section \ref{sec:result}.
Section \ref{sec:implement} gives details of our implementation, 
and we discuss in the last section how this method may be further extended. 

We make the following choices for notation: $\Int{n}$ is the additive group modulo $n$,
$\Unit{n}$ is the multiplicative group modulo $n$, and $\Int{n,l}=\Int{ln}\setminus n\Int{l}$ hence in particular
$\Int{n,1}=\Unit{n}$ and we use both interchangeably. Write $\pi_{m\to n}:\Int{m}\rightarrow\Int{n}$
for the natural projection map, when $n\mid m$, and $\pi_n:\Z\rightarrow\Int{n}$ for the reduction modulo $n$ map.
All scalar functions are also extended component-wise for any vectors.

\section{Overview}
In summary, we follow the computational method introduced by Rosenfeld \cite{Rosenfeld} in proving the conjecture for $k=7$,
and adopt the terminology\footnote{Compared to \cite{Trakulthongchai}, the two main differences are replacing $I(k,l,p)$ with 
$I(k,p,l)$ and $\delta_{cl}$ with $\delta_c$.} and techniques of \cite{Trakulthongchai}.
We outline this strategy here for completeness. 

Firstly, Rosenfeld reinterpreted the current best finite-checking result obtained by Malikiosis, Santos and Schymura \cite{Malikiosis}:
\begin{lemma}[Corollary 3, \cite{Rosenfeld}]
\label{ublemma}
    If $LRC(k-1)$ holds, then any counterexample $\ubf$ to $LRC(k)$ must have
    \[ u_1\cdots u_k < B_k \quad \text{where} \quad B_k := \paren{\frac{\binom{k+1}{2}^{k-1}}{k}}^k. \]
\end{lemma}

Hence, in order to verify $LRC(k)$, it suffices to check all speed sets such that $u_1 \cdots u_k < B_k$.
Rosenfeld then attacked this bound by generating multiple small proofs: 
for a particular prime $p$ if $\ubf$ is a counterexample, then $p$ divides $u_1 \cdots u_k$. 
These small proofs are obtained computationally with the help of the following concept.
\begin{definition}[Definition 3.1, \cite{Trakulthongchai}]
    Let $p$ be a prime and $k,l$ be positive integers.
    A speed set $\vbf\in\Int{p,l}^k$ is $(k,p,l)$-\emph{improper} if both conditions hold: 
  \begin{itemize}
    \item for any $t \in \Int{lp}$ there exists $i$ such that $\norm{\frac{tv_i}{lp}} < \frac{1}{k+1}$.
    \item for all $i$, $\gcd(lp, v_1, \dots, v_{i-1}, v_{i+1}, \dots, v_k) = 1$.
  \end{itemize}
   If $\vbf$ is not improper, it is \emph{proper}. Moreover, let $I(k,p,l)$ denotes the set of all improper speed sets.
\end{definition}

It is Rosenfeld's \cite{Rosenfeld} key insight that by restricting time $t$ to be a rational of denominator $lp$,
we can apply this time solution to every speed set $\ubf$ such that $\pi_{lp}(\ubf)=\vbf$. 

\begin{lemma}[Lemma 3.3, \cite{Trakulthongchai}]
\label{divp}
    For $k\geq3$, if $LRC(k-1)$ holds and $I(k,p,l)$ if empty for some $l$, then any counterexample
    $\ubf$ to $LRC(k)$ has $p\mid u_1\cdots u_k$. 
\end{lemma}

By accumulating emptiness proofs of $I(k,p,l)$ for a set of primes $P$, it follows that 
$\prod_{p \in P} p$ divides $v_1\cdots v_k$. If $\prod_{p \in P} p > B_k$,
we can finally conclude that counterexample to $LRC(k)$ cannot exist.

Then, the main advance of \cite{Trakulthongchai} is the following observation that allows $I(k,p,cl)$ to be computed efficiently.
We define the \textit{shadow} of $\vbf\in\Int{p,l}^k$ to be the preimage of $\vbf$ in the projection from $\Int{clp}$ to $\Int{lp}$.
Formally, $\delta_c=\pi^{-1}_{clp\to lp}$ in function terms.
From this representation it is clear that indeed $\delta_c$ also depends on $p,l$ and implicitly $k$, 
but we will use this as a shorthand and it will be clear in which domain our arguments live. 

\begin{lemma}[Lemma 3.5, \cite{Trakulthongchai}]
\label{shadowing}
We have have the inclusion
    \[I(k,p,cl)\subseteq\delta_{c}(I(k,p,l)).\]
\end{lemma}

The following lemma enables the \emph{lifting} process of the $(k,p,l)$ ansatz to the $(k,p,cl)$ ansatz which is more fine-grained, 
hopefully fine enough that we can verify that every improper speed set does indeed have a solution.
Lemma \ref{shadowing} motivates the definition of an \emph{eventually proper} speed set, 
which is the main subject of interest in our paper.
\begin{definition}
    Let $\vbf\in\Int{p,1}^k$. We say that $\vbf$ is \emph{eventually $(k,p)$-proper} if there is $c$ such 
    that $\delta_c(\vbf)$ contains no improper speed set.
\end{definition}

The concept of eventual properness simplifies our discussion and implementation;
while many speed sets in $\Int{p,1}^k$ are not proper, we conjecture that all are eventually proper. 

As the next lemma shows, the eventual properness of $\Int{p,1}^k$ is no different from the emptiness of $I(k,p,l)$ for some large $l$. 
\begin{lemma}
\label{evenpropdivp}
    Let $k\geq3$ and assume that $LRC(k-1)$ is true. If every $\vbf\in\Int{p,1}^k$ is eventually $(k,p)$-proper,
    then any counterexample $\ubf$ to $LRC(k)$ has $p\mid u_1\cdots u_k$.
\end{lemma}
\begin{proof}
    Let $c_\vbf$ be an integer such that $\delta_{c_\vbf}(\vbf)$ contains no improper speed set
    for every $\vbf\in\Int{p,1}^k$. Then take $l$ to be the least common multiple of 
    $\left\{c_\vbf : \vbf\in\Int{p,1}^k\right\}$. 
    By Lemma \ref{shadowing}, 
    \[ \delta_l(\vbf)=\delta_{l/c_\vbf}\delta_{c_\vbf}(\vbf) \] 
    contains no improper set. 
    Hence $\Int{p,l}^k=\bigcup_{\vbf\in\Int{p,1}^k}\delta_l(\vbf)$ contains no improper set, i.e., $I(k,p,l)=\emptyset$.
    By Lemma \ref{divp}, we have the conclusion.
\end{proof}


\section{Quotient modulo prime}
\label{sec:quotient}
The framework introduced in \cite{Trakulthongchai} has a bottleneck in the first phase of computation, the calculation of $I(k, p, 1)$. 
Consequently, we aim to exploit the $\Unit{p}$ symmetry of $I(k,p,l)$ to reduce the computational overhead for $I(k, p, 1)$ 
and its subsequent shadows by a factor of $p-1$. Note that this reduces the computational complexity of checking $I(k,p,1)$ 
from $\Theta(p^k)$ to $\Theta(p^{k-1})$.

Consider the relation $\sim_{lp}$ in $\Int{p,l}^k$ defined by
\[\ubf=a\vbf\quad\text{for some }a\in\Unit{lp}.\] 
The fact that $\sim_{lp}$ is an equivalence relation is a standard number theory fact.
More importantly, this relation preserves properness.

\begin{claim}
\label{firstequiv}
    If $\ubf\sim_{lp}\vbf$, then $\ubf$ is improper if and only if $\vbf$ is improper.
\end{claim}
\begin{proof}
    By symmetry, we only need to show that $\vbf$ improper implies $\ubf$ improper.
    Let $\vbf$ be improper and $\ubf=a\vbf$.
    Since the multiplier $a$ is a unit in $\Int{lp}$, meaning that $\gcd(a,lp)=1$,  we have 
    \[\gcd(lp,av_1,\ldots,av_{i-1},av_{i+1},\ldots,v_k)=\gcd(lp, v_1, \dots, v_{i-1}, v_{i+1}, \dots, v_k) = 1,\]
    so the gcd condition holds. Moreover, for any $t\in\Int{lp}$, we have
    \[\norm*{\frac{tu_i}{p}}=\norm*{\frac{t(av_i)}{p}}=\norm*{\frac{(at)v_i}{p}}\] 
    where $at\in\Int{lp}$. 
    Thus, there is some $i$ such that the last term is at least $\frac{1}{k+1}$.
    Since this is true for all $t$, the first condition holds and $\vbf$ is improper.
\end{proof}

Furthermore, $\sim_p$ preserves eventual properness.

\begin{lemma}
\label{secondequiv}
    If $\ubf\sim_p\vbf$, then $\ubf$ is eventually proper if and only if $\vbf$ is eventually proper.
\end{lemma}
\begin{proof}
    Again we only need to show one direction because of the symmetry. Let $\ubf=a\vbf$ for $a\in\Unit{p}$ and 
    assume that $\vbf$ is eventually proper, i.e., $\delta_c(\vbf)$ contains no improper speed set for some $c$.
    Let $\pi=\pi_{cp\to p}$. Notice that the restriction $\pi: \Unit{cp}\to\Unit{p}$ is surjective. 
    In particular, we can choose $b\in\Unit{cp}$ such that $\pi(b)=a$.

    Now, we fix $\ubf'\in\delta_c(\ubf)$ and choose $\vbf'=b\ubf'$. As $\pi$ is a homomorphism,
    \[\pi(\vbf')=\pi(b)\pi(\ubf')=a\pi(\ubf')=a\ubf=\vbf,\]
    so we have $\vbf'\in\delta_c(\vbf)$. Then, by assumption, $\vbf'$ is proper. 
    From Claim \ref{firstequiv}, $\ubf'$ is also proper as $\vbf'\sim_{cp}\ubf'$. 
    Therefore, every $\delta_c(\ubf)$ contains no improper speed and $\ubf$ is eventually proper.
\end{proof}

Lemma \ref{secondequiv} allows us to check eventual properness of only a single representative speed set in each
equivalence class of $\sim_p$.
It also permits changing the representatives at each step provided that the same equivalence classes are kept intact.
An easy way to pick representatives in $\Int{p,1}^k$ is to keep the first coordinate fixed to $1$,
which is what we chose for the implementation.

\section{Intermediate sieves}
\label{sec:sieves}
In this section, we denote by $\Ibar(k,p,l)$ (respectively $\Intbar{p,l}^k$) the quotient of $I(k,p,l)$ (respectively $\Int{p,l}^k$) 
by $\sim_p$. For $l>1$, we write $\ubf\sim_p\vbf$ to mean $\pi_{pl\to p}(\ubf)\sim_p\pi_{pl\to p}(\vbf)$.
It is easy to see that any natural projection onto a multiple of $p$ preserves $\sim_p$ equivalence.

\subsection{Lifting effectively}
An unimplemented idea mentioned in \cite{Trakulthongchai} is the insertion of an additional sieve. 
Observe that the cost of lifting $I'(k,p,l)$ to $I'(k,p,cl)$ is proportional to \[|I'(k,p,l)| \cdot c^k\] 
since each improper set modulo $lp$ has $c^k$ candidates (preimages modulo $clp$) to check.
When $k$ is large, the value of $c$ has greater impact on computation time. For example, when $k=11$, 
the $c=3$ lift is almost 90 times more expensive than the $c=2$ lift.

As previously discussed, we cannot avoid lifting to a multiple of $k+1$; we have to go through its prime factorization at least once.
Nevertheless, we can choose \emph{when} to perform each lift.
Since the $c=2$ lift is cheap, we can perform it multiple times in hope that we can get a smaller improper set,
i.e., $|I'(k, p, 2l)| < |I'(k,p,l)|$, before performing the expensive lift that needs to be done, e.g., $c=3$ lift when $k+1=12$.
If we succeed, we can reduce the multiplier of $3^k$ (or higher $c^k$) in the above cost formula,
shortening the overall computation time by reducing the work needed to be done in larger modulus.

We provide two example runs to illustrate this point. 
In the first run, we compare between Scheme A which is the method used to prove $k=8$ in \cite{Trakulthongchai} and
Scheme B which is designed to exploit the aforementioned cheap lifting strategy. 
Specifically, Scheme A involves lifting from $1$ to $3$ to $9$ while Scheme B is defined as in the following \emph{lifting diagram}.

A lifting diagram always starts with $S_1=I'(k,p,1)$. A horizontal arrow pointing from $S_l$ towards $S_{cl}$ indicates lifting with $c$.
Vertical arrows indicate set operations. 
The process is always performed from top to bottom, and left to right. In this notation, Scheme B is as follows:

\begin{center}
    \begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};

    % Bottom Row (T nodes) starting at the center
    \node (T1) [below=of S2] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};

    % Horizontal Arrows
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

    % Define the midpoint (M) between S2 and T1
    \coordinate (M) at ($(S2)!0.5!(T1)$);

    % Rectangular paths from S nodes merging at M (without arrowheads)
    \draw (S1) |- (M);
    \draw (S2) -- (M);
    \draw (S4) |- (M);

    % Single merged arrow dropping to T1, with "min" on the right
    \draw[->] (M) -- node[right=2pt] {$\min$} (T1);

\end{tikzpicture}
\end{center}
The operation min takes the smallest set. 
Emphasizing for clarity, this diagram shows that $S_l=I'(8,p,l)$ and $T_l=I'(8,p,lh)$, 
where $h\in\{1,2,4\}$ depends on which $S_h$ has the smallest size.

Using the same computer, Scheme A verifies the conjecture for $k=8$ in 18 seconds, while Scheme B takes 12 seconds.

The difference is more pronounced for $k=9$. Let Scheme A be $S_1\rightarrow S_2\rightarrow S_{10}$. On the other hand, let Scheme B be
\begin{center}
\begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};

    % Define midpoint between S2 and S4
    \coordinate (MidS2S4) at ($(S2)!0.5!(S4)$);

    % Middle Row (T nodes)
    \node (T1) [below=1.5cm of MidS2S4] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};

    % Define midpoint between T1 and T3
    \coordinate (MidT1T3) at ($(T1)!0.5!(T3)$);

    % Bottom Row (U nodes) starting directly under the T1-T3 midpoint
    \node (U1) [below=1.5cm of MidT1T3] {$U_1$};
    \node (U5) [right=of U1] {$U_5$};

    % Horizontal Arrows
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (T1) -- (T3);
    \draw[->] (U1) -- (U5);

    % Merge S2 and S4 down to T1
    \coordinate (M1) at ($(MidS2S4)!0.5!(T1)$);
    \draw (S2) |- (M1);
    \draw (S4) |- (M1);
    \draw[->] (M1) -- node[right=2pt] {$\min$} (T1);

    % Merge T1 and T3 down to U1
    \coordinate (M2) at ($(MidT1T3)!0.5!(U1)$);
    \draw (T1) |- (M2);
    \draw (T3) |- (M2);
    \draw[->] (M2) -- node[right=2pt] {$\min$} (U1);

\end{tikzpicture}
\end{center}
In this case, it takes under 5 seconds to run Scheme B for $p=53$ while Scheme A does not finish in 15 minutes.

See Section \ref{sec:algo} for the lifting diagrams of our verification for $k=10,11$.

\subsection{Projecting back}
Another technique at our disposal is projection. 
After we obtain $I'(k, p, l)$, projecting the speed sets back into modulo $p$ using the natural 
$\pi: \Int{lp} \to \Int{p}$ collapses some of the improper speed sets from $I'(k, p, l)$ together, 
maintaining only the structure in $\Int{p}$.
This action loses fine-grained detail of each improper speed set, but reduces the number of improper speed sets that need calculation.
We write $\pi$ in the lifting diagram to mean a projection down to $\Int{p}$.

% This idea manifests itself as the \emph{projective intersection} set operation, denoted in a lifting diagram by $\cap$, which improves upon the previous min operation. Let $A_i$ be a subset of $\Int{p,l_i}^k$ for $i=1,\ldots,n$. Then the projective intersection of $A_1,\ldots,A_n$ is
% \[\bigcap_{i=1}^n\pi_{pl_i\to p}(A_i).\] 

This operation is legal because of the following Lemma~\ref{lemmaproj}.

\begin{lemma}
  \label{lemmaproj}
  For fixed $k$ and prime $p$,
  \[ I'(k, nl, p) \subseteq \pi_{nl \to l}^{-1} \bigr( \pi_{l \to 1}^{-1} (\pi_{n \to 1} (I'(k, n, p))) \cap I'(k,p,l) \bigl).\]
\end{lemma}
\begin{proof}
  By Lemma~3.3 of \cite{Trakulthongchai}, the projection maps satisfy
  \begin{align}
    I'(k,nl,p) &\subseteq \pi_{nl \to n}^{-1}\!\paren{I'(k,n,p)}, \label{eq:proj-n}\\
    I'(k,nl,p) &\subseteq \pi_{nl \to l}^{-1}\!\paren{I'(k,l,p)}. \label{eq:proj-l}
  \end{align}

  Let $v \in I'(k,nl,p)$ be arbitrary.
  From \eqref{eq:proj-n}, we have $\pi_{nl\to n}(v) \in I'(k,n,p)$, hence
  \[
    \pi_{n\to 1}\!\left(\pi_{nl\to n}(v)\right) \;\in\; \pi_{n\to 1}\!\left(I'(k,n,p)\right).
  \]

  Since $\pi_{l\to 1}\circ\pi_{nl\to l} = \pi_{nl\to 1} = \pi_{n\to 1}\circ\pi_{nl\to n}$,  
  \[
    \pi_{l\to 1}\!\left(\pi_{nl\to l}(v)\right) \;\in\; \pi_{n\to 1}\!\left(I'(k,n,p)\right),
  \]
  i.e.\ $\pi_{nl\to l}(v) \in \pi_{l\to 1}^{-1}\!\left(\pi_{n\to 1}(I'(k,n,p))\right)$.
  Combined with \eqref{eq:proj-l}, which gives $\pi_{nl\to l}(v)\in I'(k,l,p)$, we obtain
  \[
    \pi_{nl\to l}(v)
    \;\in\;
    \pi_{l\to 1}^{-1}\!\bigl(\pi_{n\to 1}(I'(k,n,p))\bigr)
    \;\cap\;
    I'(k,l,p),
  \]
  which completes the proof.
\end{proof}

\section{Eventual properness of
  \texorpdfstring{$(\pm1,\pm2,\ldots,\pm k)$}{(+/-1, +/-2, ..., +/-k)}
}
\label{sec:onetok}
This section is improvised for the case $k=10$ or generally any $k$ where $k+1$ is prime.
With some effort in keeping track of divisibility issues, most results here can be generalized to the cases where $k+1$ is not prime,
but then the conclusions will be weaker. 

The motivation for this section is that, after applying lifting with $c=2,3$ with $I'(10,1,p)$ and taking the projective intersection,
we found that the only speed set that we cannot verify to be eventually proper is of the form
\[(\pm1,\pm2,\ldots,\pm10).\]

It is not surprising that these speed sets remain, because they will be lonely only at time $t=\frac{s}{11}$ for some $s\in\Z$ where
$11\nmid s$; it perhaps is surprising that these are the only speed sets remaining. 
Nonetheless, these speed sets can only be confirmed to be eventually proper with a $c=11$ lift, which is very costly.
Although it is unlikely that we can completely bypass these $11^{10}$ checks, 
we can do it more effectively thanks to the highly structured nature of these speed sets. 

Denote by $\fracpart{x}$ the fractional part of $x\in\mathbb{R}$ and let $A_n(x)=\lfloor n\fracpart{x}\rfloor$.
In other words, $A_n(x)$ is the integer $k$ such that $\fracpart{x}\in[k/n,(k+1)/n)$.

The following lemma is well-known.

\begin{lemma}[folklore]
\label{folklore}
    Suppose that $LRC(n)$ holds for all $n<k$. Let $p$ be a prime that divides $m$ speeds in $\vbf$, 
    where $\lceil\frac{2p}{k+1}\rceil<\frac{p}{k-m}$, and $\gcd(v_1,\ldots,v_k)=1$.
    Then $\vbf$ has the LR property.
\end{lemma}
\begin{proof}
    Assume that $v_1,\ldots,v_m$ are divisible by $p$ and $v_{m+1},\ldots,v_k$ are not. 
    Since $m<k$, $LRC(m)$ holds and we can find a time $T$ when $\norm{Tv_i}\geq\frac{1}{m+1}$ for all $i\leq m$.
    Then consider times of the form $t=T+\frac{r}{p}$ for $r\in\Zp$.
    For $i\leq m$, it follows that $\norm{tv_i}=\norm{Tv_i}\geq\frac{1}{m+1}>\frac{1}{k+1}$ as $p$ divides $v_i$ for $i\leq m$.

    For $i\geq m+1$, we note that
    \[\left\{\fracpart*{\left(T+\frac{r}{p}\right)v_m}:r\in\Zp\right\}=\left\{\fracpart*{Tv_m+\frac{r}{p}}:r\in\Zp\right\}\] 
    as $p$ is a prime that does not divide $v_m$. 
    Clearly, the latter set is a set of $p$ evenly spaced points on the unit circle, 
    so at most $\lceil\frac{2}{k+1}\cdot p\rceil$ points intersect with the interval $\left(-\frac{1}{k+1},\frac{1}{k+1}\right)$. 
    In other words, at most $\lceil\frac{2p}{k+1}\rceil$ points are not lonely for each $i=m+1,\ldots,k$. 
    
    Since there are $k-m$ such $i$, at most $(k-m)\lceil\frac{2p}{k+1}\rceil$ choices of $r\in\Zp$ are eliminated. Hence if
    \[(k-m)\left\lceil\frac{2p}{k+1}\right\rceil<p,\] 
    then there is a choice of $r$ that makes $\norm{tv_i}\geq\frac{1}{k+1}$ for all $i\geq m+1$.
\end{proof}

\begin{definition}
\label{happy}
    Let $\vbf\in\Zko^k$ and $r\in\Zp$. 
    Define the \emph{remainder vector} to be \[\rbf(x)=\left(A_{k+1}(x),A_{k+1}(2x),\ldots,A_{k+1}(kx)\right)\] 
    for $x\in\R$. We say that $\vbf$ is $(k,p)$-\emph{happy} if either of the following holds:
    \begin{itemize}
        \item (scattered) $\vbf$ contains no zero component
        \item (divisible) $\vbf$ contains at least $\frac{k+1}{2}$ zero components
        \item (lonely) there is a choice of $s\in\Zko$ and $r\in\Zp$ for which
        \[s\vbf+\rbf(r/p)\in\{1,\ldots,k-1\}^k\] when considered modulo $k+1$.
    \end{itemize}
    Otherwise, $\vbf$ is $(k,p)$-\emph{unhappy}. Let $J(k,p)$ be the set of $(k,p)$-unhappy speed sets.

\end{definition}

If not formally, at least intuitively, it is easy to see that this is just a reformulation of the previously
defined shadow of $(1,2,\ldots,k)$, and we can replace $(1,2,\ldots,k)$ with any $\wbf\in\Zp^k$ and change the definition
of the remainder vector analogously. The advantage of this formulation is that, by isolating $\rbf$ first, 
we can \emph{decouple} times of the form $t=\frac{q}{(k+1)p}$ to a partial fraction $t=\frac{s}{k+1}+\frac{r}{p}$ and only 
the first term influences the $a_ip$ term; the second term's effect is fully captured by $\rbf$. 

Consequently, we eliminate all dependence on $p$ except that coming from $\rbf(\frac{1}{p}\Zp)$ in the lonely condition. 
We can even eliminate this dependency when $p$ is large as we will mention in \ref{corlarge}.

Before we move to the application, let us first show formally that it suffices to check that $J(k,p)$ is empty to guarantee the
LR property for the shadows of $(\pm1,\pm2,\ldots,\pm k)$.

\begin{lemma}
\label{happylemma}
    Assume that $J(k,p)$ is the empty set and $k+1$ is prime. Then $(\pm1,\pm2,\ldots,\pm k)$ is eventually $(k,p)$-proper.    
\end{lemma}
\begin{proof}
    In this proof, we allow $\ubf$ to have negative speeds. First, we will prove that $(1,2,\ldots,k)$ is eventually proper. 
    Let $\ubf$ be a speed set where $u_i=a_ip+i$ for some $a_i\in\Z$ for $i=1,\ldots,k$, i.e., 
    we restrict the projection modulo $p$ to be $(1,2,\ldots,k)$ first. Consider times of the form $t=\frac{s}{k+1}+\frac{r}{p}$ 
    for $s\in\Zko$ and $r\in\Zp$. The distance of the $i$th runner from $0$ is given by
    \[\fracpart{tu_i}=\fracpart*{\left(\frac{s}{k+1}+\frac{r}{p}\right)(a_ip+i)}=\fracpart*{\frac{su_i}{k+1}+ra_i+\frac{ri}{p}}=\fracpart*{\frac{sv_i}{k+1}+\frac{ri}{p}}\] 
    where $\vbf=\ubf\mod{k+1}$, so $\vbf\in\Zko^k$.
    
    By assumption, $\vbf$ is happy. We may split into 3 cases:
    \begin{itemize}
        \item $\vbf$ is scattered. Then pick $r=0$ and $s=1$ and we have 
          \[\fracpart{tu_i}=\fracpart*{\frac{v_i}{k+1}}\in\left\{\frac{1}{k+1},\frac{2}{k+1},\ldots,\frac{k}{k+1}\right\}\] 
          for all $i$, so $\norm{tu_i}\geq\frac{1}{k+1}$ for all $i$. Hence $\ubf$ has the LR property.
        \item $\vbf$ is divisible, say $m$ speeds. 
          Since we reduced modulo $k+1$ we also have that exactly $m$ speeds of $\ubf$ are divisible by $k+1$.
          By Lemma \ref{folklore} with $p=k+1$ and $m\geq\frac{k+1}{2}$ 
          (note that the inequality
          \[\left\lceil\frac{2p}{k+1}\right\rceil=2<\frac{2(k+1)}{k-1}\leq\frac{p}{k-m}\] 
          holds),
          we have that $\ubf$ has the LR property.
        \item $\vbf$ is lonely.
          Then there is a choice of $r,s$ such $s\vbf+\rbf(r/p)\in\{1,\ldots,k-1\}^k$ in modulo $k+1$. 
          This means that $\fracpart{\frac{sv_i}{k+1}}=\frac{A_i}{k+1}$ and 
          $\fracpart{\frac{ri}{p}}\in\left[\frac{B_i}{k+1},\frac{B_i+1}{k+1}\right)$, where $C_i:=A_i+B_i\mod{k+1}$ 
          is in $\{1,\ldots,k-1\}$. Therefore,
        \[\fracpart{tu_i}=\fracpart*{\frac{sv_i}{k+1}+\frac{ri}{p}}\in\left[\frac{C_i}{k+1},\frac{C_i+1}{k+1}\right)\]
        and in particular the last set does not intersect $[0,\frac{1}{k+1})\cup(\frac{k}{k+1},1)$.  
        Since this holds for every $i$, $\ubf$ has the LR property.
    \end{itemize}
    
    Therefore $\delta_{k+1}\left((1,2,\ldots,k)\right)$ contains only proper sets, so $(1,2,\ldots,k)$ is eventually proper.
    
    The case $u_i=a_ip\pm i$ can be made into $u_i=a_ip+i$ by swapping $u_i$ with $-u_i$ for any $u_i=a_ip-i$ and noting 
    that $\norm{tu_i}=\norm{t(-u_i)}$.
\end{proof}

In practice, our most demanding work involves checking that $J(k,p)$ is empty. 
We show here that we only have to do it once to conclude this for larger $p$. 
Unfortunately, the smallest $p$ for this to be the case is around $k^3$, slightly above the largest $p$ we actually used.

\begin{corollary}
    \label{corlarge}
    Suppose that $J(k,q)$ is empty for some prime $q$. 
    Then $(\pm1,\pm2,\ldots,\pm k)$ is eventually $(k,p)$-proper for every $p\geq k(k^2-1)$.
\end{corollary}
\begin{proof}
    Note that the only condition that depends on $p$ in Definition \ref{happy} is the lonely condition. 
    Specifically, it only depends on $\rbf(\frac{1}{p}\Zp)$: if $\rbf(\frac{1}{q}\Z_q)\subseteq\rbf(\frac{1}{p}\Zp)$,
    then being $(k,q)$-happy is stronger than being $(k,p)$-happy.

    To show that this holds for any $p\geq k(k^2-1)$, we will show for such $p$, $\rbf(\frac{1}{p}\Zp)=\rbf([0,1])$.
    By pigeonhole, it suffices to show that the gaps between discontinuities in $\rbf([0,1])$ has length at least $1/p$
    because $\rbf$ only takes discrete value. Notice that $x\in[0,1]$ is a point of discontinuity only if $A_{k+1}(ix)\in\Z$ 
    for some $i\in\{1,\ldots,k\}$, that is $(k+1)ix=a$ for some $a\in\Z$. 
    Then if $x_1=\frac{a_1}{i_1(k+1)}$ and $x_2=\frac{a_2}{i_2(k+1)}$ are two distinct points of discontinuity with $x_1\neq x_2$ and
    $a_1,a_2,i_1,i_2$ integers, we have
    \[\begin{split}
        |x_1-x_2|&=\left|\frac{a_1}{i_1(k+1)}-\frac{a_2}{i_2(k+1)}\right|=\frac{1}{k+1}\left|\frac{a_1}{i_1}-\frac{a_2}{i_2}\right|\\ 
        &\geq\frac{1}{k+1}\cdot\frac{1}{k(k-1)}=\frac{1}{k(k^2-1)}\geq\frac{1}{p}.
    \end{split}\]

    Hence we conclude that $\rbf(\frac{1}{p}\Zp)=\rbf([0,1])$, and since $\frac{1}{q}\Z_q\subseteq[0,1]$, 
    we have the inclusion \[\rbf(\tfrac{1}{q}\Z_q)\subseteq\rbf([0,1])=\rbf(\displaystyle\tfrac{1}{p}\Zp).\]
    This shows that $J(k,p)$ is empty if $J(k,q)$ is empty, and the consequences follow from Lemma \ref{happylemma}.
\end{proof}

\section{Algorithms for verification}
\label{sec:algo}
From Lemmas \ref{evenpropdivp} and \ref{secondequiv}, to show that $p\mid u_1\cdots u_k$ for any 
counterexample $\ubf$ to $LRC(k)$, it suffices to check that every speed set in $\Int{p,1}^k$ is eventually proper.

The lifting diagram for the case $k=11$ is
\begin{center}
    \begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \node (S8) [right=of S4] {$S_8$};
    \node (S16) [right=of S8] {$S_{16}$};

    % Horizontal Arrows (with dotted last arrow)
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (S4) -- (S8);
    \draw[->, dotted] (S8) -- (S16); % Dotted arrow

    % Define merge points below the S nodes
    \coordinate (M4) at ($(S4)!0.5!(S4 |- 0,-2)$); % point below S4
    \coordinate (M8) at ($(S8)!0.5!(S8 |- 0,-2)$); % point below S8
    \coordinate (M16) at ($(S16)!0.5!(S16 |- 0,-2)$); % point below S16

    % Second Row (T nodes) starting centered under the merge
    % T1 is placed 1.5cm directly below S8 (the middle of the S4-S16 range)
    \node (T1) [below=1.5cm of S8] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};

    % Define the merge horizontal line at y=-1cm relative to S row
    \draw (S4) |- (M8); % Line down and then to center
    \draw (S8) -- (M8);  % Direct line down
    \draw (S16) |- (M8); % Line down and then to center

    % Single arrow dropping to T1, with "min" label
    \draw[->] (M8) -- node[right=2pt] {$\min$} (T1);
    
    % Horizontal Arrows in Second Row
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

\end{tikzpicture}
\end{center}
The dotted arrow indicates that we only proceed to compute $S_{16}$ if the previous lift was productive,
that is, if $|I'(11,p,8)|<|I'(11,p,4)|$. Note that for most primes we did not have to compute $T_9$ because $T_3$ is already empty.
In any case, if $T_3$ or $T_9$ is empty, we conclude that $p$ divides the product $u_1\cdots u_k$ of a counterexample. 

The case $k=10$ is more involved. The goal of lifting here is not to show that the last set is completely empty, 
but that there are 10 equivalence classes of speed sets remaining, and in that case we know that they must be of the form
$(\pm1,\pm2,\ldots,\pm10)$. With this in mind, the lifting diagram in this case is as follows:
\begin{center}
    \begin{tikzpicture}[
    node distance=1.5cm and 1.5cm,
    every node/.style={inner sep=2pt}
]
    % Top Row (S nodes)
    \node (S1) {$S_1$};
    \node (S2) [right=of S1] {$S_2$};
    \node (S4) [right=of S2] {$S_4$};
    \node (S8) [right=of S4] {$S_8$};

    % Middle Row (T nodes) - Vertical spacing set to 1.5cm
    \node (T1) [below=1.5cm of S8] {$T_1$};
    \node (T3) [right=of T1] {$T_3$};
    \node (T9) [right=of T3] {$T_9$};

    % Define the midpoint between T1 and T9

    % Bottom Row (U node) - Vertical spacing set to 1.5cm
    \node (U1) [below=1.5cm of T9] {$U_1$};

    % Horizontal Arrows for S Row
    \draw[->] (S1) -- (S2);
    \draw[->] (S2) -- (S4);
    \draw[->] (S4) -- (S8);

    % Horizontal Arrows for T Row
    \draw[->] (T1) -- (T3);
    \draw[->] (T3) -- (T9);

    % Merge S1 and S8 down to T1
    \draw[->] (S8) -- node[right=2pt] {$\pi$} (T1);
    \draw[->] (T9) -- node[right=2pt] {$\pi$} (U1);

    \end{tikzpicture}
\end{center}

If $U_1$ contains $10$ elements, then we check that $J(10,p)$ is empty. 
If $J(10,p)$ is, from Lemma \ref{happylemma} these remaining speed sets are eventually proper.

\section{Results}
\label{sec:result}
For the case $k=10$, let \[ P_{10} := \set{ \begin{aligned} 
    103, 131, 137, 139, 149, 151, 157, 107, 109, 127, 163, 167, 173, \\
    179, 433, 191, 193, 197, 199, 211, 223, 227, 229, 233, 239, 241, \\
    251, 257, 263, 269, 271, 277, 281, 283, 293, 307, 311, 313, 317, \\ 
    331, 337, 347, 349, 353, 359, 367, 373, 379, 383, 389, 401, 409, \\
    419, 421, 431, 433, 439, 443, 449, 457, 461 \\
    \end{aligned}
  } \]
and for the case $k=11$, let \[ P_{11} := \set{ \begin{aligned} 
      23, 131, 137, 139, 149, 151, 157, 163, 167, 173, 179, 181, 191, \\ 
      193, 197, 199, 211, 223, 227, 229, 233, 239, 241, 251, 257, 263, \\
      269, 271, 277, 281, 283, 293, 307, 311, 313, 317, 331, 337, 347, \\
      349, 353, 359, 367, 373, 379, 383, 389, 397, 401, 409, 419, 421, \\
      431, 433, 439, 443, 449, 457, 461, 463, 467, 479, 487, 491, 499, \\ 
      503, 509, 521, 523, 541, 547, 557, 563, 569, 571, 577 \\
    \end{aligned}
  } \]

Using the algorithms described in the previous section, we found that for $k\in\{10,11\}$ and $p\in P_k$, 
every $\vbf\in\Int{p,1}^k$ is eventually $(k,p)$-proper. 

\begin{theorem}
  The Lonely Runner Conjecture holds for $k=10$ and $k=11$.
\end{theorem}
\begin{proof}
  Recall that $LRC(k)$ holds for $k\leq 9$. By Lemma \ref{evenpropdivp} and the above computer verification, 
  any counterexample $\ubf$ to $LRC(10)$ must be divisible by \[\prod_{p \in P_{10}} p > e^{339} > e^{337.7} > B_{10}\] 
  where $B_{10}$ is the constant in Lemma \ref{ublemma}.
  But by the same lemma this is impossible, so no such $\ubf$ exists and $LRC(10)$ holds. 

  Similarly, for $k=11$, we also have
  \[ \prod_{p \in P_{11}} p > e^{435} > e^{434.5} > B_{11} \]
  and $LRC(11)$ follows.
\end{proof}

\section{Implementation details}
\label{sec:implement}
Rosenfeld wrote \cite{rosenfeldcode} to verify $k=7$ and the second author developed \cite{tanupatcode} to verify $k=8,9$. 
The latter code takes 
15 minutes for $k=8$ and approximately 23 hours for $k=9$. 
The first author developed \cite{mycode} to implement the algorithms in Section \ref{sec:algo}, with assistance from AI-based tools, 
to improve performance and scalability. In addition to the mathematical improvements described in Sections \ref{sec:quotient}, 
\ref{sec:sieves} and \ref{sec:onetok}, the practical aspect was also improved by refactoring the implementation to support parallel
execution and introducing more memory-efficient data structures.

These refinements dramatically improve runtime. Compared to the second author's original implementation in \cite{Trakulthongchai}, 
we proved $k=8$ in 12 seconds and $k=9$ in 181 seconds on a 10-core Apple M4 processor. 
The proofs of $k=10$ and $k=11$ were run in multiple batches, with multiple versions, and on multiple machines, 
thus making the exact time taken incomparable to other cases. The source of the computation, along with the log files, 
can be found in the first author's GitHub \cite{mycode}.

\section{Further work}
It is feasible, via a natural extension of the algorithm for $k=10$, to verify the conjecture for $k=12$.
The main bottleneck in the case $k=12$ is verifying that $J(k,p)$ is empty which now takes 2 days for each $p$ on a 14-core
Apple M3 Max processor. The size of $\Z_{k+1}^k$ is $(k+1)^k$, and this constant when $k=12$ is $10^3$ times that when $k=10$.
Nonetheless, the case $k=12$ should be practically verifiable given enough computing resources.

For $k=13$, the main bottleneck will return back to the first phase of computation, but actually might even be "more possible"
and the $k=12$ variant. 

\bibliographystyle{amsplain}
\bibliography{ref}

\end{document}

